Data Recovery and Pulse Position Modulation with a Photon Number Resolving SNSPD

### 2023-10-05 manuscript.tex
overleaf update

\usepackage{lineno}
\usepackage{todonotes}
\linenumbers % Turn off line numbering for Optica Open preprint submissions.

@@

For larger M, more data may be sent with a single optical pulse, thereby allowing a spacecrat to that is severely power limited to send more data over a high loss optical channel back to earth. The Deep Space Optical Communicaiton project managed by the Jet Propulsion Laboratory (JPL) aims to demonstrate optical communication using PPM with the Psyche spacecraft from distances of \todo[inline]{XX to XX} Au..

>>>>

\usepackage{lineno}
\usepackage{todonotes}
\usepackage{xcolor}
\usepackage{soul}
\linenumbers % Turn off line numbering for Optica Open preprint submissions.

@@

For larger M, more data may be sent with a single optical pulse, thereby allowing a spacecrat to that is severely power limited to send more data over a high loss optical channel back to earth. The Deep Space Optical Communicaiton project managed by the Jet Propulsion Laboratory (JPL) aims to demonstrate optical communication using PPM with the Psyche spacecraft from distances of \textbf{\hl{XX to XX}} Au..
